---
title: "Gene Set Analysis and Visualization"
output: html_notebook
---

Here in this code I will be trying different enrichment libraries to conduct enrichment anlysis. Each library will be given three blocks with the first block being conducting the actual enrichment and the second and third blocks that follows right after being the vizualizer. 



This first chunk conducts Gene Set Erichment Analysis with the Disease Ontology Semantic and Enrichment anlysis library. It then uses the enrichplot library to vizualize with a dotplot and a network map. 
```{r}
#Loading Necessary Libraries
library(dplyr)
library(DOSE)

#Copying over the dataframe
geneList <- SIRT5cor_nontumor
#geneList <- geneList[order(-geneList$SIRT5),]


#Creating the correct data struture for input, a named vector of correlation values for analysis. Ensured to be sorted in 
#decreasing order
genes = geneList[["SIRT5"]]
names(genes) = (geneList[["ENTREZID"]])
genes = sort(genes , decreasing = TRUE)

#GeneSetEncrichmentAnalysis using the DOSE library 
edo2 <- gseNCG(geneList = genes)

```

This chunk constructs a dotplot for the DOSE gene set enrichment analysis

```{r}
#Loading visualization libraries
library(enrichplot)

#Creating a dotplot for Visualization 
p2 <- dotplot(edo2, showCategory=30) + ggtitle("dotplot for SIRT5cor_all Data")
plot_grid(p2, ncol=1)
```

This chunk constructs a network map for the DOSE gene set enrichment anlysis

```{r}
#Creating a network map with the category as central nodes
edox <- setReadable(edo2, 'org.Hs.eg.db', 'ENTREZID')
cnetplot(edox, colorEdge = TRUE)

#cnetplot(edox,circular = TRUE, colorEdge = TRUE)
```
```{r}
library(clusterProfiler)
library(pathview)

#what <- names(genes)

keggResult <- gseKEGG(genes , organism = "hsa", keyType = "kegg")

p3 <- dotplot(keggResult, showCategory=145) + ggtitle("dotplot for SIRT5cor_all Data")
dev.new()
plot_grid(p3, ncol=1)

keggX <- setReadable(keggResult, 'org.Hs.eg.db', 'ENTREZID')
#cnetplot(keggX, colorEdge = TRUE)

heatplot(keggX)
plot(yo)

results <- keggX@result
resultsGeneSets <- keggX@geneSets
#acsorbateAldolate <- resultsGeneSets[["hsa00053"]]


```


